---
title: "Questions"
output:
word_document: default
html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

```{r}
df = read.csv(".\\Dataset\\preprocessed_data.csv")
df
```

# QUESTION 1
```{r}
data1 = df
maleNumPos = nrow(data1[data1$sex=='Male' & data1$covid_res=="Positive",])
femaleNumPos = nrow(data1[data1$sex=='Female'& data1$covid_res=="Positive",])
maleDeath = nrow(data1[data1$sex=='Male' & data1$mortality=="Died"& data1$covid_res=="Positive",])
femaleDeath = nrow(data1[data1$sex=='Female' & data1$mortality=="Died" & data1$covid_res=="Positive",])

maleDeath/maleNumPos
femaleDeath/femaleNumPos

maleNum = nrow(data1[data1$sex=="Male" ,])
femaleNum = nrow(data1[data1$sex=="Female",])

barplot(c(maleNum,maleNumPos,maleDeath,femaleNum,femaleNumPos,femaleDeath), names.arg = c("Total Males", "Cov +ve Male", "Cov +ve Male Death","Total females", "Cov +ve female", "Cov +ve female Death"), main = "Male vs Female Data", horiz = T, col = c("green","orange", "red"))
```


```{r}
data1 = df
maleNumPos = nrow(data1[data1$sex=='Male' & data1$covid_res=="Positive",])
femaleNumPos = nrow(data1[data1$sex=='Female' & data1$covid_res=="Positive",])
maleDeath = nrow(data1[data1$sex=='Male' & data1$mortality=="Died"& data1$covid_res=="Positive",])
femaleDeath = nrow(data1[data1$sex=='Female' & data1$mortality=="Died" & data1$covid_res=="Positive",])

maleDeath/maleNumPos
femaleDeath/femaleNumPos

maleNum = nrow(data1[data1$sex=='Male' ,])
femaleNum = nrow(data1[data1$sex=='Female',])

barplot(c(maleNum,maleNumPos,maleDeath,femaleNum,femaleNumPos,femaleDeath), names.arg = c("Total Males", "Cov +ve Male", "Cov +ve Male Death","Total females", "Cov +ve female", "Cov +ve female Death"), main = "Male vs Female Data", horiz = T, col = c("green","orange", "red"))

maleDeathDF = data1[data1$sex=='Male' & data1$mortality=="Died"& data1$covid_res=="Positive",]
femaleDeathDF = data1[data1$sex=='Female' & data1$mortality=="Died"& data1$covid_res=="Positive",]

 femaleDeathDF = femaleDeathDF[,c(8:24)]
  maleDeathDF = maleDeathDF[,c(8:24)]
  
  summary(maleDeathDF)
  summary(femaleDeathDF)
  
  #age not a factor as mean & median for both genders are close
  #dropping factors such as age, covid res and contact other covid
  
 # maleDeathDF = maleDeathDF[,-c(3,15,16)]
  maleDeathDF = subset(maleDeathDF, select = -c(3,15,16))
  femaleDeathDF = subset(femaleDeathDF, select = -c(3,15,16))
  

 pie(xtabs(~intubed, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male Intubed")
 pie(xtabs(~intubed, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main = "Female Intubed")
 #no significant difference
 
 pie( xtabs(~pneumonia, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male Pneumoia")
 pie( xtabs(~pneumonia, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main = "Female Pneumoia")
 #no significant difference
 
 pie(xtabs(~diabetes, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male Diabetes")
 pie(xtabs(~diabetes, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main = "Female Diabetes")
 #no significant difference
 
 pie( xtabs(~copd, data = maleDeathDF) / nrow(maleDeathDF) * 100 , main = "Male Diabetes") 
 pie( xtabs(~copd, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main =  "Female Diabetes") 
 #no significant difference
 
 pie( xtabs(~asthma, data = maleDeathDF) / nrow(maleDeathDF) * 100 , main = "Male Asthma") 
 pie( xtabs(~asthma, data = femaleDeathDF) / nrow(femaleDeathDF) * 100 , main = "Female Asthma") 
 #no significant difference
 
 pie( xtabs(~inmsupr, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male inmsupr" ) 
 pie( xtabs(~inmsupr, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main = "Female inmsupr" ) 
 #no significant difference
 
 pie( xtabs(~hypertension, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male hypertension" ) 
 pie( xtabs(~hypertension, data = femaleDeathDF) / nrow(femaleDeathDF) * 100 , main = "Female hypertension") 
 #more hypertension in women
 
 pie( xtabs(~other_disease, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male Other Disease" ) 
 pie( xtabs(~other_disease, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main = "Female Other Disease" ) 
 #no significant difference
 
 pie( xtabs(~cardiovascular, data = maleDeathDF) / nrow(maleDeathDF) * 100 , main = "Male Cardiovascular")
 pie( xtabs(~cardiovascular, data = femaleDeathDF) / nrow(femaleDeathDF) * 100, main = "Female Cardiovascular" )
 #no significant difference
 
 pie( xtabs(~obesity, data = maleDeathDF) / nrow(maleDeathDF) * 100 , main = "Male Obesity") 
 pie( xtabs(~obesity, data = femaleDeathDF) / nrow(femaleDeathDF) * 100 , main = "Female Obesity") 
 #more obesity in women
 
 pie( xtabs(~renal_chronic, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male renal chronic" )
 pie( xtabs(~renal_chronic, data = femaleDeathDF) / nrow(femaleDeathDF) * 100 , main = "Female Chronic") 
 #no significant difference
 
 pie( xtabs(~tobacco, data = maleDeathDF) / nrow(maleDeathDF) * 100 , main = "Male tobacco")
 pie( xtabs(~tobacco, data = femaleDeathDF) / nrow(femaleDeathDF) * 100 , main = "Female Tobacco") 
 #twice in men
 
 pie( xtabs(~icu, data = maleDeathDF) / nrow(maleDeathDF) * 100, main = "Male ICU" )
 pie( xtabs(~icu, data = femaleDeathDF) / nrow(femaleDeathDF) * 100 , main = "Female ICU") 
 #no significant difference
```


## QUESTION 2

Is this time of pandemic a bad period for couples to consider about pregnancy option, specific to the effect of COVID-19 on pregnant women?

```{r}
pregnant = df[df$pregnancy == "Yes",]
pregnant = pregnant[!is.na(pregnant$covid_res),]
ggplot(pregnant,aes(x=covid_res))+geom_bar(fill = "#FF6666")+xlab("Pregnant")+ggtitle("Pregnant women Covid result")
ggplot(pregnant,aes(x=mortality))+geom_bar(fill = "#FF6666")+xlab("Mortality")+ggtitle("Pregnant women died")
pregnant_positive = pregnant[pregnant$covid_res == "Positive",]
ggplot(pregnant_positive,aes(x=mortality))+geom_bar(fill = "#FF6666")+xlab("Mortality")+ggtitle("Pregnant women corona positive and died")
```

# Question3
Impact of Covid on respiratory diseases.

The respiratory diseases in the dataset are Pneumonia, Asthma, COPD (Chronic obstructive pulmonary disease), 
```{r}
respiratory = df[,c(9,13,14,23)]
respiratory

table(respiratory$covid_res, respiratory$pneumonia)
pneumonia = chisq.test(respiratory$covid_res, respiratory$pneumonia)
print(paste("Pneumonia correlation with covid results",sqrt(pneumonia$statistic/nrow(respiratory))))

table(respiratory$covid_res, respiratory$asthma)
asthma = chisq.test(respiratory$covid_res, respiratory$asthma)
print(paste("Asthma correlation with covid results",sqrt(asthma$statistic/nrow(respiratory))))

table(respiratory$covid_res, respiratory$copd)
copd = chisq.test(respiratory$covid_res, respiratory$copd)
print(paste("COPD correlation with covid results",sqrt(copd$statistic/nrow(respiratory))))
```

# Question 4
```{r}
names(df)
```

```{r}
diseases <- df[,c(9,12,13,14,15,16,17,18,19,20)] 
names(diseases)
head(diseases)
```

```{r}
library(tidyr)
```

```{r}
diseases <- drop_na(diseases)
```

```{r}
dim(diseases)
```

```{r}
table(is.na(diseases))
```

```{r}
cor_values <- matrix(nrow=10, ncol=10)
for(i in 1:10){
  for(j in 1:10){
     y = unclass(chisq.test(diseases[,i],diseases[,j]))[3]
    #print(y$p.value)
    cor_values[i,j] = y
    cor_values = matrix(cor_values, nrow=10, ncol=10)
  }
}
```

```{r}
rownames(cor_values) <- c("pneumonia", "diabetes", "copd", "asthma", "inmsupr", "hypertension", "other_disease", "cardiovascular", "obesity", "renal_chronic")

colnames(cor_values) <- c("pneumonia", "diabetes", "copd", "asthma", "inmsupr", "hypertension", "other_disease", "cardiovascular", "obesity", "renal_chronic")
cor_values
```


# Question5
One of the most challenging problem plaguing the world is Obesity and Hypertension, does these factors have any impact on the COVID-19 test result?

```{r}
Q5 = df[,c(16,19,23)]
Q5

table(respiratory$covid_res, respiratory$pneumonia)
hypertension = chisq.test(Q5$covid_res, Q5$hypertension)
print(paste("Hypertension correlation with covid results",sqrt(hypertension$statistic/nrow(Q5))))

table(respiratory$covid_res, respiratory$asthma)
Obesity = chisq.test(respiratory$covid_res, Q5$obesity)
print(paste("Obesity correlation with covid results",sqrt(Obesity$statistic/nrow(respiratory))))
```


# Question 6

```{r}
data6 = df[!is.na(df$age),]
data6 = data6[!is.na(data6$icu),]
data6 = data6[!is.na(data6$mortality),]
data6 = data6[!is.na(data6$intubed),]

range(data6$age)

dt0_20 = data6[data6$age<=20,]
dt20_40 = data6[data6$age>20 & data6$age>=40,]
dt40_60 = data6[data6$age>40 & data6$age<=60,]
dt60_80 = data6[data6$age>60 & data6$age<=80,]
dt80_100 = data6[data6$age>80 & data6$age<=100,]
dt100_120 = data6[data6$age>100 & data6$age<=120,]

pos0_20 = nrow(dt0_20[dt0_20$covid_res=="Positive",])
pos20_40 = nrow(dt20_40[dt20_40$covid_res=="Positive",])
pos40_60 = nrow(dt40_60[dt40_60$covid_res=="Positive",])
pos60_80 = nrow(dt60_80[dt60_80$covid_res=="Positive",])
pos80_100 = nrow(dt80_100[dt80_100$covid_res=="Positive",])
pos100_120 = nrow(dt100_120[dt100_120$covid_res=="Positive",])

pos0_20/nrow(dt0_20)
pos20_40/nrow(dt20_40)
pos40_60/nrow(dt40_60)
pos60_80/nrow(dt60_80)
pos80_100/nrow(dt80_100)
pos100_120/nrow(dt100_120)

library(ggplot2)

data6 = data6[data6$covid_res == "Positive", ]
ggplot(data6, aes(x = mortality, y = age, fill = mortality)) + geom_boxplot() + scale_fill_brewer(palette="Pastel2") + xlab("State")

ggplot(data6, aes(x = intubed, y = age, fill = intubed)) + geom_boxplot() + scale_fill_brewer(palette="Pastel2") + xlab("Intubed")

ggplot(data6, aes(x = icu, y = age, fill = icu)) + geom_boxplot() + scale_fill_brewer(palette="Pastel2") + xlab("ICU")

library(dplyr)

nrow(distinct(data6,id))
nrow(data6)
```


# Question 7

```{r}


df <- read.csv("Dataset\\preprocessed_data.csv")
df <- df[!is.na(df$pneumonia),]
df <- df[!is.na(df$pregnancy),]
df <- df[!is.na(df$diabetes),]
df <- df[!is.na(df$copd),]
df <- df[!is.na(df$asthma),]
df <- df[!is.na(df$inmsupr),]
df <- df[!is.na(df$hypertension),]
df <- df[!is.na(df$other_disease),]
df <- df[!is.na(df$cardiovascular),]
df <- df[!is.na(df$obesity),]
df <- df[!is.na(df$renal_chronic),]
df <- df[!is.na(df$tobacco),]
df <- df[!is.na(df$contact_other),]
df$pneumonia <- ifelse(df$pneumonia == "Yes", 1, ifelse(df$pneumonia == "No", 0, NA))
df$pregnancy<- ifelse(df$pregnancy == "Yes", 1, ifelse(df$pregnancy == "No", 0, NA))
df$diabetes<- ifelse(df$diabetes == "Yes", 1, ifelse(df$diabetes == "No", 0, NA))
df$copd <- ifelse(df$copd == "Yes", 1, ifelse(df$copd == "No", 0, NA))
df$asthma <- ifelse(df$asthma == "Yes", 1, ifelse(df$asthma == "No", 0, NA))
df$inmsupr <- ifelse(df$inmsupr == "Yes", 1, ifelse(df$inmsupr == "No", 0, NA))
df$hypertension <- ifelse(df$hypertension == "Yes", 1, ifelse(df$hypertension == "No", 0, NA))
df$other_disease <- ifelse(df$other_disease == "Yes", 1, ifelse(df$other_disease == "No", 0, NA))
df$cardiovascular <- ifelse(df$cardiovascular == "Yes", 1, ifelse(df$cardiovascular == "No", 0, NA))
df$obesity<- ifelse(df$obesity == "Yes", 1, ifelse(df$obesity == "No", 0, NA))
df$renal_chronic <- ifelse(df$renal_chronic == "Yes", 1, ifelse(df$renal_chronic == "No", 0, NA))
df$tobacco <- ifelse(df$tobacco == "Yes", 1, ifelse(df$tobacco == "No", 0, NA))
df$contact_other <- ifelse(df$contact_other_covid == "Yes", 1, ifelse(df$contact_other_covid == "No", 0, NA))
df$other_factors = df$pneumonia+df$pregnancy+df$diabetes+df$copd+df$asthma+df$inmsupr+df$hypertension+ df$other_disease+ df$cardiovascular+ df$obesity+ df$renal_chronic+df$tobacco+ df$contact_other_covid
df

```

# Question 8

```{r}
percentage = nrow(df[df$icu=='Yes' & df$other_factors == 13,])
print(percentage/nrow(df)*100)
```


## QUESTION 9 and 10

```{r}
data9 = df
data9$difference = difftime(df$entry_date,df$date_symptoms,units=c("days"))

boxplot((data9$difference) ~ data9$intubed, xlab="Intubed", ylab="Time taken to admit (in days)")
boxplot((data9$difference) ~ data9$icu, xlab="Admitted in ICU", ylab="Time taken to admit (in days)")
boxplot((data9$difference) ~ data9$mortality, xlab="Mortality", ylab="Time taken to admit (in days)")
```


```{r}
### Removing Outliers 
data9 = data9[data9$difference < 15,]
### Divide the differnce in interval of 5 days 
data9$difference_range = cut(as.numeric(data9$difference), c(0,5,10,15))

grouped_intubed = data9 %>% dplyr::select(difference_range, intubed) %>% na.omit() %>% group_by(difference_range, intubed) %>% summarise(count = n())

grouped_icu = data9 %>% dplyr::select(difference_range, icu) %>% na.omit() %>% group_by(difference_range, icu) %>% summarise(count = n())

grouped_mortality = data9 %>% dplyr::select(difference_range, mortality) %>% na.omit() %>% group_by(difference_range, mortality) %>% summarise(count = n())
```


```{r}
# Stacked barplot with multiple groups
ggplot(data=grouped_intubed, aes(x=difference_range,y=count,fill=intubed)) + geom_bar(stat="identity",position=position_dodge()) + xlab("Interval of time taken to admit (in days)") + ylab("Number of people") + theme(text = element_text(size=14),axis.text.x = element_text(size=12))


ggplot(data=grouped_icu, aes(x=difference_range,y=count,fill=icu)) + geom_bar(stat="identity",position=position_dodge()) + xlab("Interval of time taken to admit (in days)") + ylab("Number of people")+ theme(text = element_text(size=14),axis.text.x = element_text(size=12))

ggplot(data=grouped_mortality, aes(x=difference_range,y=count,fill=mortality)) + geom_bar(stat="identity",position=position_dodge()) + xlab("Interval of time taken to admit (in days)") + ylab("Number of people")+ theme(text = element_text(size=14),axis.text.x = element_text(size=12))

```


```{r}
grouped_intubed1 = data9 %>% dplyr::select(difference, intubed) %>% filter(intubed=="Yes")  %>% na.omit() %>% group_by(difference) %>% summarise(count = n()) %>% mutate(difference = as.numeric(difference))

grouped_icu1 = data9 %>% dplyr::select(difference, icu) %>% filter(icu=="Yes")  %>% na.omit() %>% group_by(difference) %>% summarise(count = n()) %>% mutate(difference = as.numeric(difference))

grouped_mortality1 = data9 %>% dplyr::select(difference, mortality) %>% filter(mortality=="Died")  %>% na.omit() %>% group_by(difference) %>% summarise(count = n()) %>% mutate(difference = as.numeric(difference))

ggplot(data=grouped_intubed1, aes(x=difference,y=count)) + geom_bar(stat="identity") + xlab("Interval of time taken to admit (in days)") + ylab("Number of people intubed")+ theme(text = element_text(size=14),axis.text.x = element_text(size=12))

ggplot(data=grouped_icu1, aes(x=difference,y=count)) + geom_bar(stat="identity") + xlab("Interval of time taken to admit (in days)") + ylab("Number of people in icu")+ theme(text = element_text(size=14),axis.text.x = element_text(size=12))

ggplot(data=grouped_mortality1, aes(x=difference,y=count)) + geom_bar(stat="identity") + xlab("Interval of time taken to admit (in days)") + ylab("Number of people died")+ theme(text = element_text(size=14),axis.text.x = element_text(size=12))
```

